%
% File acl2014.tex
%
% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{qtree}

%\setlength\titlebox{5cm}

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.


\title{A* search for shift-reduce constituent parsing}

\author{Thang Le Quang \\
  SoICT - HUST\\
  {\tt lelightwin@gmail.com} \\\And
  Yusuke Miyao \\
  National Informatic Institute\\
  {\tt Yusuke@nii.ac.jp} \\\And
  Hiroshi Noji \\
  National Informatic Institute\\
  {\tt Noji@nii.ac.jp} \\}

\date{}

\begin{document}
\maketitle

\input{abstract.tex}
\input{Section1.tex}
\input{Section2.tex}
\input{Section3.tex}
\input{Section4.tex}
\input{Section5.tex}
\input{Section6.tex}

% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2014}

\begin{thebibliography}{Reference}

\bibitem[David, 2014]{ref:2014David}
\newblock David Hall, Greg Durrett and Dan Klein. 2014.
\newblock Less Grammar, More Features.
\newblock In Proceedings of the 52nd Annual Meeting of the Association for Computational Linguistics (Volume 1: Long Papers), pages: 228-337, Baltimore, Maryland.
	
\bibitem[Zhao, 2013]{ref:2013Zhao}
\newblock Kai Zhao, Jame Cross and Liang Huang. 2013.
\newblock Optimal Incremental Parsing via Best-First Dynamic Programming.
\newblock In Proceedings of EMNLP 2013.

\bibitem[Zhu, 2012]{ref:2012Zhu}
\newblock Muhua Zhu, Yue Zhang, Wenliang Chen, Min Zhang and Jingbo Zhu. 2013.
\newblock Fast and Accurate Shift-Reduce Constituent Parsing
\newblock In proceedings of ACL 2013. Sophia, Bulgaria. August.
 
\bibitem[Huang, 2010]{ref:2010Huang}
\newblock Liang Huang and Kenji Sagae. 2010. 
\newblock Dynamic programming for linear-time incremental parsing. 
\newblock In Proceedings of ACL 2010.

\bibitem[Zhang, 2009]{ref:2009Zhang}
\newblock Yue Zhang and Stephen Clark. 2009.
\newblock Transition-based parsing of the Chinese Treebank using a global discriminative model.
\newblock In Proceedings of IWPT, Paris, France, October.

\bibitem[Xavier, 2008]{ref:2008Xavier}
\newblock Xavier Carreras, Michael Collins, and Terry Koo. 2008.
\newblock Tag, dynamic programming, and the perceptron for efficient, feature-rich parsing.
\newblock In Proceedings of CoNLL, pages 9-16, Manchester, England.

\bibitem[Huang, 2008]{ref:2008Huang}
\newblock Liang Huang. 2008.
\newblock Forest reranking: discriminative parsing with non-local features.
\newblock In Proceedings of ACL, pages 586-594, Ohio, USA.

\bibitem[Petrov, 2007]{ref:2007petrov}
\newblock Slav Petrov and Dan Klein. 2007.
\newblock Improved inference for unlexicalized parsing.
\newblock In Proceedings of HLT/NAACL, pages 404-411, Rochester, New York, April.

\bibitem[McClosky, 2006]{ref:2006Closky}
\newblock David McClosky, Eugene Charniak, and Mark Johnson. 2006.
\newblock Effective self-training for parsing.
\newblock In Proceedings of the HLT/NAACL, Main Conference, pages 152-159, New York City, USA, June.

\bibitem[Sagae, 2006]{ref:2006Sagae}
\newblock Kenji Sagae and Alon Lavie. 2006.
\newblock A best-first probabilistic shift-reduce parser
\newblock In Proceedings of the COLING/ACL, Main Conference, poster sessions, pages 691-698

\bibitem[Charniak, 2005]{ref:2005Charniak}
\newblock Eugune Charniak and Mark Johnson. 2005.
\newblock Coarse-to-fine n-best parsing and maxent discriminative reranking.
\newblock In Proceeding of ACL, pages 173-180.

\bibitem[Henderson, 2004]{ref:2004Henderson}
\newblock James Henderson. 2004.
\newblock Discriminative training of a neural network statistical parser.
\newblock In Proceedings of ACL.

\bibitem[Collins, 2004]{ref:2004Collins}
\newblock Michael Collins and Brian Roark. 2004.
\newblock Incremental parsing with the perceptron algorithm.
\newblock In Proceedings of ACL, Stroudsburg, PA, USA.

\bibitem[Taskar, 2004]{ref:2004Taskar}
\newblock Ben Taskar, Dan Klein, Michael Collins, Daphne Koller, and Chris Manning. 2004.
\newblock Max-margin parsing.
\newblock In Proceedings of EMNLP.

\bibitem[Dan2, 2003]{ref:2003Dan2}
\newblock Dan Klein and Christopher D Manning. 2003. 
\newblock Accurate Unlexicalized Parsing  
\newblock In Proceedings of ACL 2003.

\bibitem[Dan1, 2003]{ref:2003Dan1}
\newblock Dan Klein and Christopher D Manning. 2003. 
\newblock A* parsing: Fast exact Viterbi parse selection. 
\newblock In Proceedings of HLT-NAACL.

\bibitem[Collins, 2000]{ref:2000Collins}
\newblock Michael Collins. 2000.
\newblock Discriminative reranking for natural language processing.
\newblock In Proceedings of ICML, pages 175–182, Stanford, CA, USA.

\bibitem[Collins, 1999]{ref:1999Collins}
\newblock Michael Collins. 1999.
\newblock Head-driven statistical models for natural language parsing. 
\newblock Ph.D. thesis, University of Pennsylvania.

\bibitem[Collins, 1997]{ref:1997Collins}
\newblock Michael Collins. 1997.
\newblock Three generative, lexicalised models for statistical parsing. 
\newblock In Proceedings of ACL, Madrid, Spain.
 
\bibitem[Tomita, 1991] {ref:1991Tomita}
\newblock Masaru Tomita. 1991.
\newblock Generalized LR Parsing.
\newblock Kluwer Academic Publishers.

\end{thebibliography}

\end{document}
